Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2022-03-23 psy_peds_3.Rmd
ICD french codes V3

```{r}
icdCodes <- read.csv("public-data/pediatric_psychiatric_ICD10_codesV2.csv", header = TRUE, colClasses = "character") %>%
   filter( flag %in% c("originalCodes", "FrenchSpecificCodes")) %>%
   dplyr::select( disorder_group, ICD10_Code, description )
```

>>>>

```{r}
icdCodes <- read.csv("public-data/pediatric_psychiatric_ICD10_codesV3.csv", header = TRUE, colClasses = "character") %>%
   filter( flag %in% c("originalCodes", "FrenchSpecificCodes")) %>%
   dplyr::select( disorder_group, ICD10_Code, description )
```
